---
output:
  md_document:
    variant: markdown_github
---

# Purpose 

This is the README for the Financial Econometrics Practical Exam. 
This folder was created using by running:

```{r, eval = F}
fmxdat::make_project(Mac = TRUE)
```

With the folder structure for all of the questions made with the following code:
* Noting the difference between creating an html output and a pdf output

```{r, eval = F}
CHOSEN_LOCATION <- "/Users/svenwellmann/Desktop/Masters Semester 2/Financial Econometrics/Exam/"

Texevier::create_template_html(directory = glue::glue("{CHOSEN_LOCATION}20850980/Questions/"), template_name = "Question1")

Texevier::create_template(directory = glue::glue("{CHOSEN_LOCATION}20850980/Questions/"), template_name = "Question2")

Texevier::create_template(directory = glue::glue("{CHOSEN_LOCATION}20850980/Questions/"), template_name = "Question3")

Texevier::create_template_html(directory = glue::glue("{CHOSEN_LOCATION}20850980/Questions/"), template_name = "Question4")

Texevier::create_template_html(directory = glue::glue("{CHOSEN_LOCATION}20850980/Questions/"), template_name = "Question5")

Texevier::create_template(directory = glue::glue("{CHOSEN_LOCATION}20850980/Questions/"), template_name = "Question6")

Texevier::create_template_html(directory = glue::glue("{CHOSEN_LOCATION}20850980/Questions/"), template_name = "Question7")
```

Cleaning the environment, loading packages and sourcing all functions:

```{r}
rm(list = ls()) # Clean your environment:
gc() # garbage collection 

pacman::p_load("xts", "tidyverse", "tbl2xts", "PerformanceAnalytics", "lubridate", "glue", "rmsfuns", "fmxdat", "tidyr", "devtools", "readr", "TTR",
               "DEoptimR", "robustbase", "rportfolios", "RiskPortfolios", "fitHeavyTail", "quadprog", "cowplot", "FactoMineR", "factoextra", "ggdendro")
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```


# Question 1 

## Fund Performance 

## Code used for Figures and Tables

```{r}
rm(list = ls()) # Clean your environment:
gc() # garbage collection 
```
```{r}
pacman::p_load("tidyverse", "lubridate")
```
```{r}
list.files('Question1/code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
```

## Data 

The raw data files were placed in their respective question data folders 





# Question 2 

## Yield Spreads

We must load in the data from the data folder within the question folder. 

```{r}
list.files('Question2/code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
loc2 <- "Questions/Question2/data/"

SA_bonds <- read_rds(glue::glue("{loc2}SA_Bonds.rds"))
BE_Infl <- read_rds(glue::glue("{loc2}BE_Infl.rds")) # 10yr Break even inflation estimate
bonds_2y <- read_rds(glue::glue("{loc2}bonds_2y.rds")) # International 2yr spreads
bonds_10y <- read_rds(glue::glue("{loc2}bonds_10y.rds")) # International 10yr spreads
usdzar <- read_rds(glue::glue("{loc2}usdzar.rds"))
ZA_Infl <- read_rds(glue::glue("{loc2}ZA_Infl.rds"))
IV <- read_rds(glue::glue("{loc2}IV.rds")) # Volatility Index
```

Then with the data we must clean all the data we want to use and creature new features we can graph.
For the SA_Bonds we need to gather the data into tidy format to make plotting easier. 
We will also clean the inflation data and exchange rate data. 

```{r}
pacman::p_load("tidyverse", "lubridate", "fmxdat")
```


## Historical Bond Yields

This will look at bond returns historically and how they have moved. This will then be filtered to look at bond yields since 2020 and assess their movements. 

```{r}
# Transforming the Bonds data into tidy format for plotting
SA_bonds_clean <- SA_bonds %>%  
    arrange(date) %>% 
    gather(Ticker, Yield, -date)
```


```{r}
SA_Bond_All <- SA_bonds_clean %>% 
    ggplot() +
    geom_line(aes(date, Yield, color = Ticker)) +
    fmxdat::theme_fmx(title.size = ggpts(30),
                      subtitle.size = ggpts(28),
                      caption.size = ggpts(25),
                      CustomCaption = T) + 
  fmxdat::fmx_cols() + 
  labs(x = "", 
       y = "Bond Yields", 
       caption = "Note:\nCalculation own",
       title = "Bond Yields in South Africa across the 3 month, 2 year and 10 year maturities") + 
    guides(color = F)

fmxdat::finplot(SA_Bond_All, x.vert = T, x.date.type = "%Y", x.date.dist = "2 years")
```

This graph shows that over the last 20+ years bond yields have actually decreased relatively. With the largest decline that of the shortest maturity bond, the 3-month bond. What we can see in this graph is that the bond yields before 2020 were moving with one another. Since 2020 you can see a divergence of the Bond Yields, taking us to our next analysis: Yield Spreads. 

## Historical Bond Yield Spreads

Bond spreads across the same 20+ year range.

Below we create the bond spread features  and make the data long.

```{r}
SA_Spreads <- SA_bonds %>% 
    arrange(date) %>% 
    group_by(date) %>% 
    mutate(YS_2Yr_3M = ZA_2Yr-SA_3M, 
           YS_10Yr_3M = ZA_10Yr-SA_3M, 
           YS_10Yr_2Yr = ZA_10Yr-ZA_2Yr) %>% 
    ungroup() %>% 
    pivot_longer(c("YS_2Yr_3M", "YS_10Yr_3M", "YS_10Yr_2Yr"), names_to = "Spreads", values_to = "Rates") 
```

These spreads are then graphed using fmxdat's finplot. 

```{r}
bond_spreads <- SA_Spreads %>% 
    ggplot() +
    geom_line(aes(date, Rates, colour = Spreads), alpha = 0.8) +
    labs(title = "Short,Mid and Long Term SA Spreads", y = "Spreads (Yields)", x ="") +
    fmxdat::theme_fmx() + 
    fmxdat::fmx_cols()

fmxdat::finplot(bond_spreads, x.date.type = "%Y", x.vert = TRUE, x.date.dist = "2 years")
```
This plot confirms that the spreads do face a significant spike in 2020, this can be seen especially for the spread of the long-term (10 year) bond yield.
Now we look further into the data from 2020 until now. 

## Looking closer at 2020

```{r}
bond_spreads_since2020 <- SA_Spreads %>% 
    filter(date >= as.Date("2020/01/01")) %>% 
    ggplot() +
    geom_line(aes(date, Rates, colour = Spreads), alpha = 0.8) +
    labs(title = "Short, Mid and Long Term SA Spreads", y = "Spreads (Yields)", x ="") +
    fmxdat::theme_fmx() + 
    fmxdat::fmx_cols()

fmxdat::finplot(bond_spreads_since2020, x.date.type = "%Y%m", x.vert = TRUE )
```


## 10-year Break-even inflation estimate vs SA Inflation

Here we join the Break-even inflation with the monthly inflation in South Africa, find the first date that there is information on all the data and then plot the data.

```{r}
# First find the first available data range
BE_inflation_start <- BE_Infl %>% pull(date) %>% first

BE_Inflation <- rbind(ZA_Infl, 
                      BE_Infl) %>% 
    arrange(date) %>% 
    filter(date >= BE_inflation_start)

```

```{r}
BE_Inflation_plot <- BE_Inflation %>% 
    ggplot() +
    geom_line(aes(date, Price, colour = Name), alpha = 0.8) +
    labs(title = "Break-even 10 year Inflation and SA Inflation", 
         y = "Percent", 
         x ="", 
         subtitle = "") +
    fmxdat::theme_fmx(title.size = ggpts(25), subtitle.size = ggpts(20)) + 
    fmxdat::fmx_cols()

fmxdat::finplot(BE_Inflation_plot, x.date.type = "%Y%m", x.vert = TRUE)
```

## USD-ZAR Exchange rate and Bond yields

The below graph shows how the USD-ZAR exchange rate and the medium and long-term bond yields moved in sync at the beginning of 2020. The exchange rate lowered from its peak in 2020 while the long-term bond yields remained at their high level. 

```{r}
# Left_join daily bond yields and the USD-ZAR exchange rate
YS_usd_zar <- left_join(SA_bonds %>% 
    arrange(date) %>% 
    group_by(date) %>% 
    mutate(YS_2Yr_3M = ZA_2Yr-SA_3M, 
           YS_10Yr_3M = ZA_10Yr-SA_3M, 
           YS_10Yr_2Yr = ZA_10Yr-ZA_2Yr), 
    usdzar %>% 
        arrange(date) %>% 
        rename(EX = Price) %>% 
        select(-Name), 
    by = "date") %>% 
    pivot_longer(c("YS_2Yr_3M", "YS_10Yr_3M", "YS_10Yr_2Yr", "EX"), names_to = "Spreads", values_to = "Rates") %>% 
    select(date, Spreads, Rates)
```

Below is the Historical plot of Bond spreads and the USD-ZAR exchange rate. What is noticeable is that before 2010 the yield spreads move in opposite direction to the exchange rate. This change after 2010 as we witness the exchange rate climb steadily and in 2020 the exchange rate and yield spreads move together.

```{r}
YS_usd_zar_plot <- YS_usd_zar %>% 
    ggplot() +
    geom_line(aes(date, Rates, colour = Spreads), alpha = 0.8) +
    facet_wrap(~Spreads, scales = "free_y") +
    guides(alpha = "none") + 
    labs(title = "Short, Mid and Long Term SA Spreads", y = "Spreads (Yields)", x ="", subtitle = "Including USD/ZAR Exchange Rate") +
    fmxdat::theme_fmx(title.size = ggpts(25), subtitle.size = ggpts(20)) + 
    fmxdat::fmx_cols()

fmxdat::finplot(YS_usd_zar_plot, x.date.type = "%Y%m", x.vert = TRUE)
```

## Volatility Indices and SA Yield Spread Graph

```{r}
# Compare SA Spreads to VIX

SA_Spreads_Int_VIX <- rbind(SA_Spreads %>% select(date, Spreads, Rates),
                            IV %>% rename(Spreads = Name, Rates = Price)) %>% 
    arrange(date) %>% filter(date >= as.Date("2020/01/01"))
```


Volatility Index Graph

```{r}
# PLot Spreads and Indices on Seperate Axis

SA_Spreads_Int_VIX_plot <- SA_Spreads_Int_VIX %>% 
    ggplot() +
    geom_line(aes(date, Rates, colour = Spreads), alpha = 0.8) +
    facet_wrap(~Spreads, scales = "free_y") +
    guides(alpha = "none") + 
    labs(title = "Volatility Indices and SA Yield Spreads", x ="", subtitle = "Including VIX, V2X and VXEEM Volatility Indices") +
    fmxdat::theme_fmx(title.size = ggpts(25), subtitle.size = ggpts(18), legend.size = ggpts(15)) + 
    fmxdat::fmx_cols()

fmxdat::finplot(SA_Spreads_Int_VIX_plot, x.date.type = "%Y%m", x.vert = TRUE)
```

We can see that the spike in the VIX caused a shift in all the yield spreads. To further put htis into context we will graph the 10-year - 2-year yield spread of RSA and international countries in order to see the links between yield spreads and the VIX.

## Foreign Yields and VIX

```{r}
US_Spreads <- cbind(bonds_2y %>% 
                        filter(Name %in% "US_2yr") %>% 
                        filter(date >= as.Date("2020/01/01")), 
                    bonds_10y %>% 
                        filter(Name %in% "US_10Yr") %>% 
                        arrange(date) %>% 
                        filter(date >= as.Date("2020/01/01")) %>% 
                        select(-date) %>% 
                        rename(US10 = Name)) %>% 
    arrange(date) %>% 
    mutate(YS_10Yr_2Yr_US = Bond_10Yr - Bond_2Yr) %>% 
    select(date, YS_10Yr_2Yr_US) %>% 
    pivot_longer(YS_10Yr_2Yr_US, names_to = "Spreads", values_to = "Rates")

UK_Spreads <- cbind(bonds_2y %>% 
                        filter(Name %in% "UK_2yr") %>% 
                        filter(date >= as.Date("2020/01/01")), 
                    bonds_10y %>% 
                        filter(Name %in% "UK_10Yr") %>% 
                        arrange(date) %>% 
                        filter(date >= as.Date("2020/01/01")) %>% 
                        select(-date) %>% 
                        rename(US10 = Name)) %>% 
    arrange(date) %>% 
    mutate(YS_10Yr_2Yr_UK = Bond_10Yr - Bond_2Yr) %>% 
    select(date, YS_10Yr_2Yr_UK) %>% 
    pivot_longer(YS_10Yr_2Yr_UK, names_to = "Spreads", values_to = "Rates")


All_spreads <- rbind(SA_Spreads_Int_VIX %>% select(date, Spreads, Rates) %>% filter(Spreads %in% c("YS_10Yr_2Yr", "VIX")),
      US_Spreads, 
      UK_Spreads) %>%  
    arrange(date)

```

Graph All spreads with the VIX

```{r}
All_Spreads_Int_VIX_plot <- All_spreads %>% 
    ggplot() +
    geom_line(aes(date, Rates, colour = Spreads), alpha = 0.8) +
    facet_wrap(~Spreads, scales = "free_y") +
    guides(alpha = "none") + 
    labs(title = "International Yield Spreads with the VIX", x ="", subtitle = "RSA, UK and US Yield Spreads") +
    fmxdat::theme_fmx(title.size = ggpts(25), subtitle.size = ggpts(18), legend.size = ggpts(15)) + 
    fmxdat::fmx_cols()

fmxdat::finplot(All_Spreads_Int_VIX_plot, x.date.type = "%Y%m", x.vert = TRUE)
```


# Question 3 

## Portfolio Construction

First we have to load in the data

```{r}
list.files('Question/Question3/code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

loc3 <- "Questions/Question3/data/"

usdzar <- read_rds(glue::glue("{loc2}usdzar.rds"))
T40 <- read_rds(glue::glue("{loc3}T40.rds"))
RebDays <- read_rds(glue::glue("{loc3}Rebalance_days.rds"))
```

## What have we done

To get the portfolio returns I use the Safe_Return.portfolio function for each portfolio based on their separate weightings.I make this into a function in order granulate the ALSI and SWIX into different sector and index, which can be made into a list of objects that this function can be mapped over. The first part of the function is to make sure the weights of each granulation sums to 1. This is done by normalising the vectors of weights with their own summation.

For the returns we impute the NA values from the impute_missing_returns function. First we will us this function with no granulation to see the cumulative returns across all sectors and indices.

Both of these functions can be found withing this questions code folder.

```{r}
portfolio_cum_return <- portfolio_return_function(T40) %>% group_by(Portfolio) %>% 
    mutate(cumreturn_Rand = (cumprod(1 + Returns))) %>% 
    mutate(cumreturn_Rand = cumreturn_Rand/first(cumreturn_Rand))

portfolio_cum_return_plot <- portfolio_cum_return %>% 
    ggplot() +
    geom_line(aes(date, cumreturn_Rand, colour = Portfolio), alpha = 0.8) + 
    fmxdat::fmx_cols() + 
    labs(title = "Cumulative Returns for ALSI and SWIX", y = "Cumulative Returns", x = "") + 
    fmxdat::theme_fmx(title.size = ggpts(25))

finplot(portfolio_cum_return_plot)
```

I want to plot the different weights per sector through time. For this I need the values below from the function above. Unfortunately I short-cutted this in order to save time instead of being able to extract it from the function itself. 

```{r include=FALSE}
# First we get the weights of the ALSI and SWIX into xts format
j200_weights <- T40 %>% select(date, Tickers, J200) %>% spread(Tickers, J200) %>% tbl_xts()
j400_weights <- T40 %>% select(date, Tickers, J400) %>% spread(Tickers, J400) %>% tbl_xts()

# Then we get the returns for all the Tickers into xts format
stock_returns <- T40 %>% select(date, Tickers, Return) %>% spread(Tickers, Return) 

# Forcing the NA values to 0
# We can do this as NA weights are just 0
j200_weights[is.na(j200_weights)] <- 0
j400_weights[is.na(j400_weights)] <- 0

# For NA's in returns it is safer to impute values for the NA's
stock_returns <- impute_missing_returns(stock_returns, impute_returns_method = "Drawn_Distribution_Collective")
stock_returns <- stock_returns %>% tbl_xts()


J200_RetPort <- rmsfuns::Safe_Return.portfolio(stock_returns, 
                                               weights = j200_weights, lag_weights = TRUE,
                                               verbose = TRUE, contribution = TRUE, 
                                               value = 1, geometric = TRUE) 

J400_RetPort <- rmsfuns::Safe_Return.portfolio(stock_returns, 
                                             weights = j400_weights, 
                                             lag_weights = TRUE,
                                             verbose = TRUE, contribution = TRUE, 
                                             value = 1, geometric = TRUE) 

# Need to clean and save the data

# Clean and save portfolio returns and weights:
J200_Contribution <- J200_RetPort$"contribution" %>% xts_tbl() 

J200_BPWeight <- J200_RetPort$"BOP.Weight" %>% xts_tbl() 
    
J200_BPValue <- J200_RetPort$"BOP.Value" %>% xts_tbl()
    
# Clean and save portfolio returns and weights:
J400_Contribution <- J400_RetPort$"contribution" %>% xts_tbl() 
    
J400_BPWeight <- J400_RetPort$"BOP.Weight" %>% xts_tbl()
    
J400_BPValue <- J400_RetPort$"BOP.Value" %>% xts_tbl() 

names(J200_Contribution) <- c("date", names(J200_RetPort$"contribution"))
names(J200_BPWeight) <- c("date", names(J200_RetPort$"BOP.Weight"))
names(J200_BPValue) <- c("date", names(J200_RetPort$"BOP.Value"))
names(J400_Contribution) <- c("date", names(J400_RetPort$"contribution"))
names(J400_BPWeight) <- c("date", names(J400_RetPort$"BOP.Weight"))
names(J400_BPValue) <- c("date", names(J400_RetPort$"BOP.Value"))
```

I got the weight vectors and subset the dataframes by the tickers that are a part of each category. I then summed across these Tickers to get their total weight per row. This allowed me to plot the different weights rolling through time. 

```{r}
resources_tickers <- T40 %>% filter(Sector %in% "Resources") %>% pull(Tickers) %>% unique
industrials_tickers <- T40 %>% filter(Sector %in% "Industrials") %>% pull(Tickers) %>% unique
financials_tickers <- T40 %>% filter(Sector %in% "Financials") %>% pull(Tickers) %>% unique

J400_BPWeight$resource_weight <- rowSums(J400_BPWeight[, resources_tickers])
J400_BPWeight$industrial_weight <- rowSums(J400_BPWeight[, industrials_tickers])
J400_BPWeight$financial_weight <- rowSums(J400_BPWeight[, financials_tickers])

J200_BPWeight$resource_weight <- rowSums(J200_BPWeight[, resources_tickers])
J200_BPWeight$industrial_weight <- rowSums(J200_BPWeight[, industrials_tickers])
J200_BPWeight$financial_weight <- rowSums(J200_BPWeight[, financials_tickers])
```


An interesting look into the portfolios is to see which industries are weighted highest between the SWIX and ALSI. Below is a plot of their different factor weights through time. We can see that since 2020 the ALSI lowered their weighting of Financial stocks and increased their weighting of resource stocks in comparison to the SWIX. 

* ALSI (J200)

```{r}
J200_BPWeight %>% 
  select(date, resource_weight, industrial_weight, financial_weight) %>% 
  tbl_xts() %>% 
  .[endpoints(.,'months')] %>% 
  chart.StackedBar() 
  
```

* SWIX (J400)

```{r}
J400_BPWeight %>% 
  select(date, resource_weight, industrial_weight, financial_weight) %>% 
  tbl_xts() %>% 
  .[endpoints(.,'months')] %>% 
  chart.StackedBar() 
```

Now we can use this function across a list of the different sectors and plot the results.

```{r}
# Compare Sectors for ALSI and SWIX

sectors <- T40 %>% pull(Sector) %>% unique()
sector_return <- list()

for(i in 1:length(sectors)){
    # Loop through sectors and calculate returns and cumulative returns
    sector_return[[i]] <- portfolio_return_function(T40, sector = sectors[i]) %>% group_by(Portfolio) %>% 
    mutate(cumreturn_Rand = (cumprod(1 + Returns))) %>% # Start at 1
        mutate(cumreturn_Rand = cumreturn_Rand/first(cumreturn_Rand)) %>% 
        mutate(Sector = sectors[i])
}



# Rename tibbles
names(sector_return) <- sectors
sector_return

# Combine Dataframes
sectors_cum_return <- rbind(sector_return[[1]], sector_return[[2]], sector_return[[3]]) %>% arrange(date)
    
sectors_cum_return_plot <- sectors_cum_return %>% 
    ggplot() +
    geom_line(aes(date, cumreturn_Rand, colour = Portfolio), alpha = 0.8) + facet_wrap(~Sector) + fmxdat::fmx_cols() + 
    labs(title = "Cumulative Returns per Sector for ALSI and SWIX", y = "Cumulative Returns", x = "") + 
    fmxdat::theme_fmx(title.size = ggpts(25))

finplot(sectors_cum_return_plot)
```

We can also run this funciton across the different indices and plot the results. 

```{r}
# Compare indices for ALSI and SWIX
indices <- T40 %>%  pull(Index_Name) %>% na.omit(.) %>%  unique()
indices_return <- list()

for(i in 1:length(indices)){
    # Loop through sectors and calculate returns and cumulative returns
    indices_return[[i]] <- portfolio_return_function(T40,index = indices[i]) %>% group_by(Portfolio) %>% 
    mutate(cumreturn_Rand = (cumprod(1 + Returns))) %>% # Start at 1
mutate(cumreturn_Rand = cumreturn_Rand/first(cumreturn_Rand)) %>% 
    mutate(Index = indices[i])
}

# Rename tibbles
names(indices_return) <- indices

# Combine Dataframes
indices_cum_return <- rbind(indices_return[[1]], indices_return[[2]], indices_return[[3]]) %>% arrange(date)
    
indices_cum_return_plot <- indices_cum_return %>% 
        ggplot() +
        geom_line(aes(date, cumreturn_Rand, colour = Portfolio), alpha = 0.8) + facet_wrap(~Index) + fmxdat::fmx_cols() + 
        labs(title = "Cumulative Returns per Index for ALSI and SWIX", y = "Cumulative Returns", x = "") +
        fmxdat::theme_fmx(title.size = ggpts(25))

finplot(indices_cum_return_plot)
```

## Stratify the returns by high and low volatility

First we find the bounds of our lower and higher quantiles at 20\%

```{r}
zar <-  usdzar  %>% 
    filter(date > ymd(20080101)) %>% 
    mutate(Return = Price/lag(Price) - 1) %>% 
    filter(date > first(date)) %>% 
    select(-c(Price, Name))

ZARSD <- zar %>% 
    mutate(YearMonth = format(date, "%Y%B")) %>% 
    group_by(YearMonth) %>% 
    summarise(SD = sd(Return)*sqrt(52)) %>% 
    # Top Decile Quantile overall (highly volatile month for ZAR:
    mutate(TopQtile = quantile(SD, 0.8), BotQtile = quantile(SD, 0.2))

Hi_Vol <- ZARSD %>% filter(SD > TopQtile) %>% pull(YearMonth)

Low_Vol <- ZARSD %>% filter(SD < BotQtile) %>% pull(YearMonth)
```

Here we create a function to compare performances suring times of low or high volatility

```{r}
# Create generic function to compare performance:
Perf_comparisons <- function(Idxs, YMs, Alias){
  # For stepping through uncomment:
  # YMs <- Hi_Vol
  Unconditional_SD <- Idxs %>% 
      group_by(Tickers) %>% 
      mutate(Full_SD = sd(Return) * sqrt(252)) %>% 
      filter(YearMonth %in% YMs) %>% 
      summarise(SD = sd(Return) * sqrt(252), across(.cols = starts_with("Full"), .fns = max)) %>% 
      arrange(desc(SD)) %>% mutate(Period = Alias) %>% 
      group_by(Tickers) %>% 
      mutate(Ratio = SD / Full_SD)
  
  Unconditional_SD
}
```

We have to get our portfolio returns, winsorize the returns to make sure there are no large outliers and then we compare. We then create a table for both volatility of the ALSI and SWIX during periods of both low and high exchange rate volatility.

```{r}
# Get portfolio returns
ALSI_SWIX <- portfolio_return_function(T40)

# Prepare and Winzorise Returns
ALSI_SWIX <- ALSI_SWIX %>% 
    group_by(Portfolio) %>% 
    mutate(YearMonth = format(date, "%Y%B")) %>% 
    rename(Tickers = Portfolio, Return = Returns) %>% 
    group_by(Tickers) %>% 
    mutate(Top = quantile(Return, 0.99), Bot = quantile(Return, 0.01)) %>% 
    mutate(Return = ifelse(Return > Top, Top, ifelse(Return < Bot, Bot, Return))) %>% ungroup()

perf_hi <- Perf_comparisons(ALSI_SWIX, YMs = Hi_Vol, Alias = "High_Vol")

perf_lo <- Perf_comparisons(ALSI_SWIX, YMs = Low_Vol, Alias = "Low_Vol")

# Creating tables in kable
perf_hi_table <- perf_hi %>% kable() %>% add_header_above(c("High Volatility" = 5))
perf_lo_table <- perf_lo %>% kable() %>% add_header_above(c("Low Volatility" = 5))

perf_hi_table
```

Printing the volatilities in the low volatility periods.

```{r}
perf_lo_table
```


## Construct a capped portfolio

For the analysis of the capped portfolios we have to first find the effective rebalancing days and coalesce any NA's to zero

```{r}
# first filter out the Effective rebalance days 
effective_rebDays <- RebDays %>% filter(Date_Type %in% "Effective Date")

rebalance_ALSI <- T40 %>% filter(date %in% effective_rebDays$date) %>% 
    mutate(RebalanceTime = format(date, "%Y%B")) %>% 
    select(date, Tickers, Return, J200, RebalanceTime) %>% 
    rename(weight = J200) %>% 
    mutate(weight = coalesce(weight , 0))

# Checking if there are any NA's left
any(is.na(rebalance_ALSI$weight))
```

First we will cap the ALSI at 10\%. For this we need to get the weights and returns.

```{r}
# Apply Proportional_Cap_Foo to ALSI to get capped return for cap of 10%
ALSI_capped_10 <- rebalance_ALSI %>% 
  group_split(RebalanceTime) %>% 
  map_df(~Proportional_Cap_Foo(., W_Cap = 0.1) ) %>% 
  select(-RebalanceTime)
 
ALSI_wts_10 <- ALSI_capped_10 %>% 
  tbl_xts(cols_to_xts = weight, spread_by = Tickers)

ALSI_rts_10 <- T40 %>% 
    filter(Tickers %in% unique(ALSI_capped_10$Tickers)) %>% 
    tbl_xts(cols_to_xts = Return, spread_by = Tickers)

# Make NA values into 0's
ALSI_wts_10[is.na(ALSI_wts_10)] <- 0

ALSI_rts_10[is.na(ALSI_rts_10)] <- 0

ALSI_capped_10 <- rmsfuns::Safe_Return.portfolio(R = ALSI_rts_10, weights = ALSI_wts_10, lag_weights = T) %>% 
    xts_tbl() %>% 
    rename(ALSI_10 = portfolio.returns)
```

We repeat this for the ALSI but at a cap of 6\%.

```{r}
# Apply Proportional_Cap_Foo to ALSI to get capped return for cap of 6%
ALSI_capped_6 <- rebalance_ALSI %>% 
  group_split(RebalanceTime) %>% 
  map_df(~Proportional_Cap_Foo(., W_Cap = 0.06) ) %>% 
  select(-RebalanceTime)
 
ALSI_wts_6 <- ALSI_capped_6 %>% 
  tbl_xts(cols_to_xts = weight, spread_by = Tickers)

ALSI_rts_6 <- T40 %>% 
    filter(Tickers %in% unique(ALSI_capped_6$Tickers)) %>% 
    tbl_xts(cols_to_xts = Return, spread_by = Tickers)

# Make NA values into 0's
ALSI_wts_6[is.na(ALSI_wts_6)] <- 0

ALSI_rts_6[is.na(ALSI_rts_6)] <- 0

ALSI_capped_6 <- rmsfuns::Safe_Return.portfolio(R = ALSI_rts_6, weights = ALSI_wts_6, lag_weights = T) %>% 
    xts_tbl() %>% 
    rename(ALSI_6 = portfolio.returns)
```

We plot the cumulative return for the ALSI with a 10\% cap and a 6\% cap on individual stocks. 

```{r}
# Both ALSI Capped indexes
capped_ALSI <- left_join(ALSI_capped_10, ALSI_capped_6, by = "date") %>% 
  pivot_longer(c("ALSI_6", "ALSI_10"), names_to = "Portfolio", values_to = "returns")

capped_ALSI_plot <- capped_ALSI %>% 
    group_by(Portfolio) %>%
    mutate(Idx = cumprod(1 + returns)) %>% 
    ggplot() + 
    geom_line(aes(date, Idx, colour = Portfolio), alpha = 0.8) + 
    labs(subtitle = "ALSI capped at 10% and 6%", x = "", y = "Cumulative Return") + 
    fmx_cols() + 
    fmxdat::theme_fmx(subtitle.size = ggpts(20))

finplot(capped_ALSI_plot)
```

The analysis above is then repeated for the SWIX.

```{r}
# Apply Proportional_Cap_Foo to SWIX to get capped return for cap of 10%
rebalance_SWIX <- T40 %>% filter(date %in% effective_rebDays$date) %>% 
    mutate(RebalanceTime = format(date, "%Y%B")) %>% 
    select(date, Tickers, Return, J400, RebalanceTime) %>% 
    rename(weight = J400) %>% 
    # There are 27 NA's in this so we coalesce them to 0
    mutate(weight = coalesce(weight , 0))

SWIX_capped_10 <- rebalance_SWIX %>% 
  group_split(RebalanceTime) %>% 
  map_df(~Proportional_Cap_Foo(., W_Cap = 0.1) ) %>% 
  select(-RebalanceTime)
 
SWIX_wts_10 <- SWIX_capped_10 %>% 
  tbl_xts(cols_to_xts = weight, spread_by = Tickers)

SWIX_rts_10 <- T40 %>% 
    filter(Tickers %in% unique(SWIX_capped_10$Tickers)) %>% 
    tbl_xts(cols_to_xts = Return, spread_by = Tickers)

# Make NA values into 0's
SWIX_wts_10[is.na(SWIX_wts_10)] <- 0

SWIX_rts_10[is.na(SWIX_rts_10)] <- 0

SWIX_capped_10 <- rmsfuns::Safe_Return.portfolio(R = SWIX_rts_10, weights = SWIX_wts_10, lag_weights = T) %>% 
    xts_tbl() %>% 
    rename(SWIX_10 = portfolio.returns)

# Apply Proportional_Cap_Foo to SWIX to get capped return for cap of 6%
SWIX_capped_6 <- rebalance_SWIX %>% 
  group_split(RebalanceTime) %>% 
  map_df(~Proportional_Cap_Foo(., W_Cap = 0.06) ) %>% 
  select(-RebalanceTime)
 
SWIX_wts_6 <- SWIX_capped_6 %>% 
  tbl_xts(cols_to_xts = weight, spread_by = Tickers)

SWIX_rts_6 <- T40 %>% 
    filter(Tickers %in% unique(SWIX_capped_6$Tickers)) %>% 
    tbl_xts(cols_to_xts = Return, spread_by = Tickers)

# Make NA values into 0's
SWIX_wts_6[is.na(SWIX_wts_6)] <- 0

SWIX_rts_6[is.na(SWIX_rts_6)] <- 0

SWIX_capped_6 <- rmsfuns::Safe_Return.portfolio(R = SWIX_rts_6, weights = SWIX_wts_6, lag_weights = T) %>% 
    xts_tbl() %>% 
    rename(SWIX_6 = portfolio.returns)

# Both ALSI Capped indexes
capped_SWIX <- left_join(SWIX_capped_10, SWIX_capped_6, by = "date") %>% 
  pivot_longer(c("SWIX_6", "SWIX_10"), names_to = "Portfolio", values_to = "returns")

capped_SWIX_plot <- capped_SWIX %>% 
    group_by(Portfolio) %>%
    mutate(Idx = cumprod(1 + returns)) %>% 
    ggplot() + 
    geom_line(aes(date, Idx, colour = Portfolio), alpha = 0.8) + 
    labs(subtitle = "SWIX capped at 10% and 6%", x = "", y = "Cumulative Return") + 
    fmx_cols() + 
    fmxdat::theme_fmx(subtitle.size = ggpts(20))

finplot(capped_SWIX_plot)
```

The function used to construct a capped portfolio and determine its performance is found within the code folder of this question.

# Question 4 

## Volatility Comparison

First we have to load in the data and do some data manipulations:

```{r}
# Load the data from Q3
T40 <- read_rds(glue::glue("{loc3}T40.rds"))

# Find the top 40 stocks from the last date 
T40_tickers <- T40 %>% arrange(date) %>% 
    filter(date == dplyr::last(date)) %>% 
    arrange(desc(J200)) %>%  
    top_n(40, J200) %>% 
    pull(Tickers) %>% 
    unique()

# Clean up the names of the data 
ALSI_T40 <- T40 %>% 
    filter(Tickers %in% T40_tickers) %>% 
    mutate(Tickers = gsub("SJ Equity", "", Tickers))
```

We first plot the returns over time to see if there are any outliers and how large they are. Below we can see there are some with large outliers but nothing too major so we will not limit the data. 

```{r}
ggplot(ALSI_T40) + geom_line(aes(x = date, y = Return, color = Tickers, alpha = 0.9)) + ggtitle("Equity Log Returns: SA") + guides(alpha = FALSE)
```

We need wide data to find the PCA's. There are NA values in the data so we use the impute_missing_returns function from Question 3. We impute values according to own distribution as if we impute across the whole dataframe it will bias the PCA analysis. 

```{r}
# Make data wide
ALSI_T40_wide <- ALSI_T40 %>% select(date, Tickers, Return) %>% spread(Tickers, Return)

# impute missing values
ALSI_T40_wide <- impute_missing_returns(ALSI_T40_wide, impute_returns_method = "Drawn_Distribution_Own") %>% select(-date)
```


## PCA

The scree plot below is the best visual illustration of the contribution of the top 10 PCA factors to explaining the variation. The top PCA factor explains just over 20 percent of the variation with the top 5 explaining almost 50 percent of the variation.

```{r}
# Run PCA
ALSI_T40_pca <- PCA(ALSI_T40_wide, graph = FALSE)

fviz_screeplot(ALSI_T40_pca, ncp = 10)
```

The figure below shows how the individual stocks contribute to the first PCA factor. 

```{r}
fviz_contrib(ALSI_T40_pca, choice = "var", axes = 1) 
```

We do the same as above except for the second PCA.

```{r}
fviz_contrib(ALSI_T40_pca, choice = "var", axes = 2)
```

We now visualise the direction of the variables across the first and second PCA.

```{r}
fviz_pca_var(pca, col.var = "contrib", repel = T) + theme_minimal()
```

# Rolling correlation

To calculate constituent correlations through time I calculate the correlation matrix of the top 40 constituents in the ALSI, which derived from a Ledoit-Wolf shrunk matrix. I then use the auxiliary functions loaded from Nico's gist. 

```{r}
# We use this due to heavy tails in the data
Sigma <- fitHeavyTail::fit_mvt(ALSI_T40_wide) %>% .$cov

corr <- cov2cor(Sigma)
distmat <- ((1 - corr)/2)^0.5

cluster <- cluster::agnes(dist(distmat), method = "ward")

```

Below we have complex comovement structures using a dendogram, colouring several groups that are of note.

```{r}
cluster_aux()

hcdata <- dendro_data_k(cluster, 4)
p <- plot_ggdendro(hcdata, direction = "lr", expand.y = 0.2)

cols <- c("#a9a9a9", "#1f77b4", "#ff7f0e", "#2ca02c", "#AD3636")
p <- plot_ggdendro(hcdata, direction = "tb", scale.color = cols, label.size = 2.5, branch.size = 0.5, expand.y = 0.2)
p <- p + theme_void() + expand_limits(x = c(-1, 32))

p + labs(title = "Dendogram of Top 40 ALSI stocks", caption = "Dendogram created using Ward distances and AGNES clustering")
```


## Stratify for periods of high volatility 

```{r}
# Determine Periods of high volatility

ALSI_T40_vol <- ALSI_T40 %>% 
  select(date, Tickers, Return) %>% 
  arrange(date) %>% 
  mutate(YearMonth = format(date, "%Y%B")) %>% 
  group_by(YearMonth) %>% 
  summarise(SD = sd(Return)*sqrt(52)) %>%
  mutate(TopQtile = quantile(SD, 0.8))

# There are 33 months of high volatility 
Hi_Volatility <- ALSI_T40_vol %>% filter(SD > TopQtile) %>% pull(YearMonth)

# Extract these months
ALSI_T40_volatile <- ALSI_T40 %>% 
  select(date, Tickers, Return) %>% 
  mutate(YearMonth = format(date, "%Y%B")) %>% 
  filter(YearMonth %in% Hi_Vol)
```

I have stratified the data for highly volatile periods and for these periods found the PCA's. Below it is evident that that the first PCA hasa  larger contribution that the PCA of the full data, reaching almost 25 percent. All of the graph sabove are reproduced for the volatile periods below.

```{r}
# Make data wide
ALSI_T40_volatile_wide <- ALSI_T40_volatile %>% select(date, Tickers, Return) %>% spread(Tickers, Return)

# impute missing values
ALSI_T40_volatile_wide <- impute_missing_returns(ALSI_T40_volatile_wide, impute_returns_method = "Drawn_Distribution_Own") %>% select(-date)

ALSI_T40_volatile_wide_pca <- PCA(ALSI_T40_volatile_wide, graph = FALSE)

fviz_screeplot(ALSI_T40_volatile_wide_pca)
```


```{r}
fviz_contrib(ALSI_T40_volatile_wide_pca, choice = "var", axes = 1) 
```


```{r}
fviz_pca_var(ALSI_T40_volatile_wide_pca, col.var = "contrib", repel = T) + theme_minimal()
```

And then the correlation clustering for highly volatile periods:

```{r}
# We use this due to heavy tails in the data
Sigma_vol <- fitHeavyTail::fit_mvt(ALSI_T40_volatile_wide) %>% .$cov

corr_vol <- cov2cor(Sigma_vol)
distmat_vol <- ((1 - corr_vol)/2)^0.5

cluster_vol <- cluster::agnes(dist(distmat_vol), method = "ward")

```

Below we have complex comovement structures using a dendogram, colouring several groups that are of note.

```{r}
hcdata_vol <- dendro_data_k(cluster_vol, 4)
p_vol <- plot_ggdendro(hcdata_vol, direction = "lr", expand.y = 0.2)

cols <- c("#a9a9a9", "#1f77b4", "#ff7f0e", "#2ca02c", "#AD3636")
p_vol <- plot_ggdendro(hcdata, direction = "tb", scale.color = cols, label.size = 2.5, branch.size = 0.5, expand.y = 0.2)
p_vol <- p_vol + theme_void() + expand_limits(x = c(-1, 32))

p_vol + labs(title = "Dendogram of Top 40 ALSI stocks during highly volatile periods", caption = "Dendogram created using Ward distances and AGNES clustering")
```


# Question 5 

## Volatility and GARCH estimates

The South African rand (ZAR) has over the past few years been one of the most volatile currencies;

The ZAR has generally performed well during periods where G10 currency carry trades have been favourable and these currency valuations relatively cheap. Globally, it has been one of the currencies that most benefit during periods where the Dollar is comparatively strong, indicating a risk-on sentiment.


First we have to load in the data

```{r}
loc5 <- "Questions/Question5/data/"

cncy <- read_rds(glue::glue("{loc5}currencies.rds"))
cncy_Carry <- read_rds(glue::glue("{loc5}cncy_Carry.rds"))
cncy_value <- read_rds(glue::glue("{loc5}cncy_value.rds"))
cncyIV <- read_rds(glue::glue("{loc5}cncyIV.rds"))
bbdxy <- read_rds(glue::glue("{loc5}bbdxy.rds"))

```


```{r}
pacman::p_load(sugrrants, rugarch)
```


Test for conditional heteroskedasticity

```{r}
test_cond_het_func <- function(data = zar_ret){
    
    Plotdata <- data %>% 
        mutate(Returns = dlogret, 
               Returns_Sqd = dlogret^2, 
               Returns_Abs = abs(dlogret))
        
        Plotdata <- Plotdata %>% 
        pivot_longer(c("Returns", "Returns_Sqd", "Returns_Abs"), names_to = "ReturnType", values_to = "Returns")
        
        ret_plot <- Plotdata %>% ggplot() + 
        geom_line(aes(x = Date, y = Returns, colour = ReturnType), alpha = 0.8) + 
            
        ggtitle("Return Type Persistence") + 
        facet_wrap(~ReturnType, nrow = 3, ncol = 1, scales = "free") + 
            
        guides(alpha = "none", colour = "none") + 
        fmxdat::theme_fmx()
        
        acf_1 <- Plotdata %>% 
        ggplot() + geom_acf(aes(x = ..lag.., y = dlogret)) + theme_bw() + labs(subtitle = "ACF of Dlog Ret", y = "")
        acf_2 <- Plotdata %>% 
        ggplot() + geom_acf(aes(x = ..lag.., y = dlogret^2)) + theme_bw() + labs(subtitle = "ACF of Sqaured Dlog Ret", y = "")
        acf_3 <- Plotdata %>% 
        ggplot() + geom_acf(aes(x = ..lag.., y = abs(dlogret))) + theme_bw() + labs(subtitle = "ACF of Absolute value of Dlog Ret", y = "")
        
        acf_plots <- plot_grid(acf_1, acf_2, acf_3, nrow = 1)
        
        box_stats <- Box.test(data$dlogret^2, type = "Ljung-Box", lag = 12)

    out <- list(`Return Plots` = ret_plot,
                `ACF Plots` = acf_plots,
                `Box Statistics` = box_stats)
    out
    
}
```

Fit GARCH function

```{r}
vol_func <- function(data = zar_ret, model = "sGARCH"){
    
    data <- data %>% select(Date, dlogret) %>%  tbl_xts()
    
    gjrgarch11 = ugarchspec(variance.model = list(model = model, 
                                              
                                              garchOrder = c(1, 1)), 
                        
                        mean.model = list(armaOrder = c(1, 0), include.mean = TRUE), 
                        
                        distribution.model = c("norm", "snorm", "std", "sstd", "ged", "sged", "nig", "ghyp", "jsu")[3])
# Now to fit, I use as.matrix and the data - this way the plot functions we will use later will work.
garchfit2 = ugarchfit(spec = gjrgarch11, data = as.matrix(data)) 

garchfit2
}
```

Select Best Garch Model

```{r}

vol_select_func <- function(data = zar_ret){
    data <- data %>% select(Date, dlogret) %>%  tbl_xts()
    models = 1:4
    model.list = list()
    
    for (p in models) { 
        garchfit = ugarchspec(
        variance.model = list(model = c("sGARCH","gjrGARCH","eGARCH","apARCH")[p], garchOrder = c(1, 1)), 

        mean.model = list(armaOrder = c(1, 0), include.mean = TRUE), 

        distribution.model = c("norm", "snorm", "std", "sstd", "ged", "sged", "nig", "ghyp", "jsu")[1])

        garchfit1 = ugarchfit(spec = garchfit,data=as.numeric(data)) 

        model.list[[p]] = garchfit1
        }
    names(model.list) <- c("sGARCH","gjrGARCH","eGARCH","apARCH")

    fit.mat = sapply(model.list, infocriteria)  
    
    # Note: sapply can apply a function (infocriteria here) to a list...
    rownames(fit.mat) = rownames(infocriteria(model.list[[1]]))
    fit.mat
}
```

Plot Smoothed Ret^2

```{r}
vol_plot_func <- function(data = zar_ret, fit = garch_fit){
    # To view the conditional variance plot, use:
    sigma <- sigma(fit) %>% xts_tbl() 
    colnames(sigma) <- c("date", "sigma") 
    sigma <- sigma %>% mutate(Date = as.Date(date))

    Plotdata <- data %>% 
        mutate(Returns = dlogret, 
               Returns_Sqd = dlogret^2, 
               Returns_Abs = abs(dlogret)) %>% 
        pivot_longer(c("Returns", "Returns_Sqd", "Returns_Abs"), names_to = "ReturnType", values_to = "Returns")

gg <- Plotdata %>% 
    ggplot() + 
    geom_line(data = Plotdata %>% 
                  filter(ReturnType == "Returns_Sqd") %>% 
                  select(Date, Returns) %>% 
                  unique() %>% 
                  mutate(Returns = sqrt(Returns)), 
              aes(x = Date, y = Returns), alpha = 0.8) + 
    geom_line(data = sigma, aes(x = Date, y = sigma), color = "red", size = 2, alpha = 0.8) + 
    labs(title = "Comparison: Returns Sigma vs Sigma from Garch", x = "", y = "Comparison of estimated volatility") + 
    fmxdat::theme_fmx(title = ggpts(25))
    fmxdat::finplot(gg, y.pct = T, y.pct_acc = 1)

}
```

Determine whether ZAR is more volatile

```{r}
zar_ret <- cncy %>% 
    filter(date > as.Date("2009-12-31")) %>% 
    filter(Name %in% "SouthAfrica_Cncy") %>% 
    mutate(dlogret = log(Price) - lag(log(Price))) %>% 
    filter(date > first(date)) %>% 
    rename(Date = date)

# Test for GARCH effects
test_cond_het_func(zar_ret)
```

Find best model

```{r}
best_mod <- vol_select_func(zar_ret)
best_mod
```

Fit Model

```{r}
garch_fit <- vol_func(zar_ret, "gjrGARCH")
# Model Coefficients
garch_fit@fit$matcoef
```

Plot Model

```{r}
vol_plot_func(data = zar_ret, fit = garch_fit)
```

Find highest vols

```{r}
max_vol <- cncy %>% filter(date > as.Date("2009-12-31")) %>% arrange(date) %>% 
    group_by(Name) %>% 
    mutate(dlogret = log(Price) - lag(log(Price))) %>% filter(date > first(date)) %>% rename(Date = date) %>% mutate(vol = dlogret^2) %>% 
    summarise(`Mean_Vol` = mean(vol)) %>% 
    arrange(desc(Mean_Vol)) %>% top_n(10, Mean_Vol)
```

ZAR Vol and cncyIV

```{r}
# Compare Smoothed ZAR Vol to mean Global VOL

# Calculate Mean Global VOL
mean_vol <- cncyIV %>% filter(date > as.Date("2009-12-31")) %>% 
    group_by(date) %>% 
    summarise(mean_vol = mean(Price)) %>% 
        mutate(Global_vol = mean_vol/max(mean_vol))

# Wrangle Sigma into dataframe
sigma <- sigma(garch_fit) %>% xts_tbl() 
colnames(sigma) <- c("date", "sigma") 
sigma <- sigma %>% mutate(Date = as.Date(date)) %>% 
    mutate(ZAR_sigma = sigma/max(sigma))%>% left_join(., mean_vol, by = "date")

# Plot prop of max volatility to be comparable
q4_p2 <- sigma %>% select(-date) %>% 
    pivot_longer(c("ZAR_sigma", "Global_vol"), names_to = "Vol_type", values_to = "VOL") %>% 
    ggplot() +
    geom_line(aes(Date, VOL, colour = Vol_type)) +
    labs(title = "Comparison of ZAR Cleaned Volatility and Mean Currency Volatility", x = "", 
         y = "Prop of Max Vol") +
    fmx_cols() +
    theme_fmx(title.size = ggpts(25)) 

finplot(q4_p2)
```

ZAR Returns during high Carry Trade Returns

```{r}
# Stratify for high carry trade periods and check ZAR Returns
zar_ret <- cncy %>% filter(date > as.Date("2009-12-31") & date < as.Date("2020-01-01")) %>% filter(Name %in% "SouthAfrica_Cncy") %>% 
    mutate(dlogret = log(Price) - lag(log(Price))) %>% filter(date > dplyr::first(date)) %>% rename(Date = date)

# Find high carry trade periods
carry_dat <- cncy_Carry %>% filter(date > as.Date("2009-12-31") & date < as.Date("2020-01-01")) %>% mutate(dlogret = log(Price) - lag(log(Price))) %>% filter(date > dplyr::first(date)) %>% rename(Date = date) 

df_carry <- carry_dat %>% 
  mutate(YearMonth = format(Date, "%Y%B")) %>% 
  group_by(YearMonth) %>%
  mutate(TopQtile = quantile(dlogret, 0.9))

Hi_carry <- df_carry %>% filter(dlogret > TopQtile) %>% pull(YearMonth)

# Find low value periods
value_dat <- cncy_value %>% 
    filter(date > as.Date("2009-12-31") & date < as.Date("2020-01-01")) %>% mutate(dlogret = log(Price) - lag(log(Price))) %>% filter(date > dplyr::first(date)) %>% rename(Date = date) 


df_value <- value_dat %>% 
  mutate(YearMonth = format(Date, "%Y%B")) %>% 
  group_by(YearMonth) %>%
  mutate(BotQtile = quantile(dlogret, 0.1))

Low_value <- df_value %>% filter(dlogret < BotQtile) %>% pull(YearMonth)

# Find Strong Dollar periods

basket_dat <- bbdxy %>% 
    filter(date > as.Date("2009-12-31") & date < as.Date("2020-01-01")) %>% mutate(dlogret = log(Price) - lag(log(Price))) %>% filter(date > dplyr::first(date)) %>% rename(Date = date) 


df_basket <- basket_dat %>% 
  mutate(YearMonth = format(Date, "%Y%B")) %>% 
  group_by(YearMonth) %>%
  mutate(TopQtile = quantile(dlogret, 0.9))

High_Basket <- df_basket %>% filter(dlogret > TopQtile) %>% pull(YearMonth)

# Compare mean returns

df_zar_carry <- zar_ret %>% 
    mutate(YearMonth = format(Date, "%Y%B")) %>% 
    filter(YearMonth %in% Hi_carry) %>% ungroup() %>% 
    summarise(Mean_Ret = mean(dlogret)) %>% 
    mutate(Type = "Carry-Trade")

df_zar_value <- zar_ret %>% 
    mutate(YearMonth = format(Date, "%Y%B")) %>% 
    filter(YearMonth %in% Low_value) %>% ungroup() %>% 
    summarise(Mean_Ret = mean(dlogret)) %>% 
    mutate(Type = "Value")

df_zar_basket <- zar_ret %>% 
    mutate(YearMonth = format(Date, "%Y%B")) %>% 
    filter(YearMonth %in% High_Basket) %>% ungroup() %>% 
    summarise(Mean_Ret = mean(dlogret)) %>% 
    mutate(Type = "Basket")

df_norm <- zar_ret %>% ungroup() %>% 
    summarise(Mean_Ret = mean(dlogret)) %>% 
    mutate(Type = "Normal")

rbind(df_norm, df_zar_carry, df_zar_value, df_zar_basket)
```

# Question 6

## MSCI Funds


```{r}
loc6 <- "Questions/Question6/data/"


msci <- read_rds(glue::glue("{loc6}msci.rds"))
bonds <- read_rds(glue::glue("{loc6}bonds_10y.rds"))
comms <- read_rds(glue::glue("{loc6}comms.rds"))
```

```{r}
msci %>% pull(Name) %>% unique()
bonds %>% pull(Name) %>% unique()
comms %>% pull(Name) %>% unique()
```

* Over the past decade, the return profiles of different asset classes (Equities, Commodities, Real Estate and Bonds) have increased in their convergence (i.e., diversification by holding different asset classes have reduced).
* Show how these comovements have increased in the past decade;
* Show to what extent these return profiles have homogenized by considering the commonality of the sources of returns over time.
* In your answer, be creative in using visual and statistical measures to convey the issue of
how co-movement have changed over time.


```{r}
# Calculate Returns for Assets

# Calculate All World Index Returns
stock <- msci %>% filter(Name %in% "MSCI_ACWI") %>% 
    mutate(dlogret = log(Price) - log(lag(Price))) %>% 
    mutate(scaledret = (dlogret - 
    mean(dlogret, na.rm = T))) %>% 
    filter(date > dplyr::first(date)) %>% select(-Price) %>%
    filter(date > as.Date("2005-06-20")) %>% 
    rename(MSCI_ACWI = scaledret) %>%
    select(date, MSCI_ACWI)
# Calculate Japanese 10 Year Bond Returns
bond <- bonds %>% filter(Name %in% "EURO_10Yr") %>% 
    mutate(dlogret = Bond_10Yr/lag(Bond_10Yr) - 1) %>%
    mutate(scaledret = (dlogret - 
    mean(dlogret, na.rm = T))) %>% 
    filter(date > dplyr::first(date)) %>% select(-Bond_10Yr) %>%
    filter(date > as.Date("2005-06-20"))%>% 
    rename(EURO_10Yr = scaledret) %>%
    select(date, EURO_10Yr)
# Calculate US Real Estate Returns
re <- msci %>% filter(Name %in% "MSCI_USREIT") %>% 
    mutate(dlogret = log(Price) - log(lag(Price))) %>% 
    mutate(scaledret = (dlogret - 
    mean(dlogret, na.rm = T))) %>% 
    filter(date > dplyr::first(date)) %>% select(-Price) %>%
    filter(date > as.Date("2005-06-20")) %>% 
    rename(MSCI_USREIT = scaledret) %>%
    select(date, MSCI_USREIT)
# Calculate Brent Crude Oil Returns
comm <- comms %>% filter(Name %in% "Oil_Brent" ) %>% 
    mutate(dlogret = log(Price) - log(lag(Price))) %>% 
    mutate(scaledret = (dlogret - 
    mean(dlogret, na.rm = T))) %>% 
    filter(date > dplyr::first(date)) %>% select(-Price) %>%
    filter(date > as.Date("2005-06-20")) %>% 
    rename(Oil_Brent = scaledret) %>% 
    select(date, Oil_Brent)
# Combine and wrangle for DCC models
assets <- left_join(stock, bond, by = c("date")) %>% 
    left_join(., re, by = c("date")) %>% 
    left_join(., comm, by = c("date")) %>% 
    tbl_xts()
```


```{r}
# Renaming DCC code from Tutorial
renamingdcc <- function(ReturnSeries, DCC.TV.Cor) {
  
ncolrtn <- ncol(ReturnSeries)
namesrtn <- colnames(ReturnSeries)
paste(namesrtn, collapse = "_")

nam <- c()
xx <- mapply(rep, times = ncolrtn:1, x = namesrtn)
# Now let's be creative in designing a nested for loop to save the names corresponding to the columns of interest.. 

# TIP: draw what you want to achieve on a paper first. Then apply code.

# See if you can do this on your own first.. Then check vs my solution:

nam <- c()
for (j in 1:(ncolrtn)) {
for (i in 1:(ncolrtn)) {
  nam[(i + (j-1)*(ncolrtn))] <- paste(xx[[j]][1], xx[[i]][1], sep="_")
}
}

colnames(DCC.TV.Cor) <- nam

# So to plot all the time-varying correlations wrt SBK:
 # First append the date column that has (again) been removed...
DCC.TV.Cor <- 
    data.frame( cbind( date = index(ReturnSeries), DCC.TV.Cor)) %>% # Add date column which dropped away...
    mutate(date = as.Date(date)) %>%  tbl_df() 

DCC.TV.Cor <- DCC.TV.Cor %>% gather(Pairs, Rho, -date)

DCC.TV.Cor

}
```

```{r}
# Determine whether autocorrelation using March Test
MarchTest(assets)
```

```{r}
# Use tutorial code to fit gjrGARCH (1,0) and DCC (1,1)

# Set GARCH specifications
uspec <- ugarchspec(variance.model = list(model = "gjrGARCH", 
    garchOrder = c(1, 1)), mean.model = list(armaOrder = c(1, 
    0), include.mean = TRUE), distribution.model = "sstd")

multi_univ_garch_spec <- multispec(replicate(ncol(assets), uspec))

# Set DCC specifications
spec.dcc = dccspec(multi_univ_garch_spec, dccOrder = c(1, 1), 
    distribution = "mvnorm", lag.criterion = c("AIC", "HQ", "SC", 
        "FPE")[1], model = c("DCC", "aDCC")[1])  

# Parallelize 
cl = makePSOCKcluster(10)

# Fit GARCH
multf = multifit(multi_univ_garch_spec, assets, cluster = cl)

# Fit DCC
fit.dcc = dccfit(spec.dcc, data = assets, solver = "solnp", 
    cluster = cl, fit.control = list(eval.se = FALSE), fit = multf)

# Check Model
RcovList <- rcov(fit.dcc) 
covmat = matrix(RcovList, nrow(assets), ncol(assets) * ncol(assets), 
    byrow = TRUE)
mc1 = MCHdiag(assets, covmat)
```

```{r}
# Wrangle DCC Output
dcc.time.var.cor <- rcor(fit.dcc)
dcc.time.var.cor <- aperm(dcc.time.var.cor, c(3, 2, 1))
dim(dcc.time.var.cor) <- c(nrow(dcc.time.var.cor), ncol(dcc.time.var.cor)^2)

# Rename DCC Output

dcc.time.var.cor <- renamingdcc(ReturnSeries = assets, DCC.TV.Cor = dcc.time.var.cor)
```


```{r}
# Create Plots

# Stocks
g1 <- ggplot(dcc.time.var.cor %>% filter(grepl("MSCI_ACWI_", Pairs), 
    !grepl("_MSCI_ACWI", Pairs))) + geom_line(aes(x = date, y = Rho, 
    colour = Pairs)) + theme_hc() + labs(subtitle = "Dynamic Conditional Correlations: MSCI_ACWI", x = "", y = "") +
    fmx_cols() + theme_fmx(subtitle.size = ggpts(25), legend.size = ggpts(15))

# Bonds
g2 <- ggplot(dcc.time.var.cor %>% filter(grepl("EURO_10Yr_", Pairs), 
    !grepl("_EURO_10Yr", Pairs))) + geom_line(aes(x = date, y = Rho, 
    colour = Pairs)) + theme_hc() + labs(subtitle="Dynamic Conditional Correlations: EURO_10Yr", x = "", y = "") +
    fmx_cols() + theme_fmx(subtitle.size = ggpts(25), legend.size = ggpts(15))

# Real Estate
g3 <- ggplot(dcc.time.var.cor %>% filter(grepl("MSCI_USREIT_", Pairs), 
    !grepl("_MSCI_USREIT", Pairs))) + geom_line(aes(x = date, y = Rho, 
    colour = Pairs)) + theme_hc() + labs(subtitle = "Dynamic Conditional Correlations: MSCI_USREIT", x = "", y = "") +
    fmx_cols() + theme_fmx(subtitle.size = ggpts(25), legend.size = ggpts(15))


# Commodities
g4 <- ggplot(dcc.time.var.cor %>% filter(grepl("Oil_Brent_", Pairs), 
    !grepl("_Oil_Brent", Pairs))) + geom_line(aes(x = date, y = Rho, 
    colour = Pairs)) + theme_hc() + labs(subtitle = "Dynamic Conditional Correlations: Oil_Brent", x = "", y = "") +
    fmx_cols() + theme_fmx(subtitle.size = ggpts(25), legend.size = ggpts(15))

g1

```


```{r}
g2
```


```{r}
g3
```


```{r}
g4
```


```{r}
# Go-GARCH following the Tutorial

# GARCH Specifications
spec.go <- gogarchspec(multi_univ_garch_spec, 
                       distribution.model = 'mvnorm', 
                       ica = 'fastica') 
# Parallelize
cl <- makePSOCKcluster(10)
# Fit GARCH
multf <- multifit(multi_univ_garch_spec, assets, cluster = cl)

#GO-GARCH Specifications
fit.gogarch <- gogarchfit(spec.go, 
                      data = assets, 
                      solver = 'hybrid', 
                      cluster = cl, 
                      gfun = 'tanh', 
                      maxiter1 = 40000, 
                      epsilon = 1e-08, 
                      rseed = 100)

# Go-Garch Fit
print(fit.gogarch)
```



```{r}
# Wrangle Output
gog.time.var.cor <- rcor(fit.gogarch)
gog.time.var.cor <- aperm(gog.time.var.cor,c(3,2,1))
dim(gog.time.var.cor) <- c(nrow(gog.time.var.cor), ncol(gog.time.var.cor)^2)

# Rename Output
gog.time.var.cor <-
renamingdcc(ReturnSeries = assets, DCC.TV.Cor = gog.time.var.cor)


# Create Plots

# Stocks
g2_1 <- ggplot(gog.time.var.cor %>% filter(grepl("MSCI_ACWI_", Pairs), 
    !grepl("_MSCI_ACWI", Pairs))) + geom_line(aes(x = date, y = Rho, 
    colour = Pairs)) + theme_hc() + labs(subtitle = "Go-Garch: MSCI_ACWI", x = "", y = "") +
    fmx_cols() + theme_fmx(subtitle.size = ggpts(25), legend.size = ggpts(15))

# Bonds
g2_2 <- ggplot(gog.time.var.cor %>% filter(grepl("EURO_10Yr_", Pairs), 
    !grepl("_EURO_10Yr", Pairs))) + geom_line(aes(x = date, y = Rho, 
    colour = Pairs)) + theme_hc() + labs(subtitle="Go-Garch: EURO_10Yr", x = "", y = "") +
    fmx_cols() + theme_fmx(subtitle.size = ggpts(25), legend.size = ggpts(15))

# Real Estate
g2_3 <- ggplot(gog.time.var.cor %>% filter(grepl("MSCI_USREIT_", Pairs), 
    !grepl("_MSCI_USREIT", Pairs))) + geom_line(aes(x = date, y = Rho, 
    colour = Pairs)) + theme_hc() + labs(subtitle = "Go-Garch: MSCI_USREIT", x = "", y = "") +
    fmx_cols() + theme_fmx(subtitle.size = ggpts(25), legend.size = ggpts(15))


# Commodities
g2_4 <- ggplot(gog.time.var.cor %>% filter(grepl("Oil_Brent_", Pairs), 
    !grepl("_Oil_Brent", Pairs))) + geom_line(aes(x = date, y = Rho, 
    colour = Pairs)) + theme_hc() + labs(subtitle = "Go-GARCH: Oil_Brent", x = "", y = "") +
    fmx_cols() + theme_fmx(subtitle.size = ggpts(25), legend.size = ggpts(15))

g2_1
```


# Question 7

## Portfolio Construction


```{r}
loc7 <- "Questions/Question7/data/"

MAA <- read_rds(glue::glue("{loc7}MAA.rds")) %>% select(-Name)
msci <- read_rds(glue::glue("{loc6}msci.rds")) %>% filter(Name %in% c("MSCI_ACWI", "MSCI_USA", "MSCI_RE", "MSCI_Jap")) %>% rename(Ticker = Name)
```


```{r}
# Combine Assets classes
comb_assets <- rbind(MAA, msci) %>% arrange(date)

# Looking back 3 years utilising fmxdat::safe_year_min
comb_assets_3_years <- comb_assets %>% group_by(Ticker) %>% filter(date == fmxdat::safe_year_min(last(date), N = 3)) %>% pull(Ticker) %>% unique()

# Filter all Tickers that have data for at least previous 3 years and find the earliest starting date across all Tickers
Start_Date <- comb_assets %>% 
    filter(Ticker %in% comb_assets_3_years) %>% 
    group_by(Ticker) %>% 
    summarise(date = dplyr::first(date)) %>% 
    pull(date) %>% 
    first()

# Unique month end dates for all assets since the start date 
EOM_dates <- comb_assets %>% 
    filter(Ticker %in% comb_assets_3_years) %>% 
    filter(date >= Start_Date) %>% 
    select(date) %>% 
    unique() %>% 
    mutate(YM = format(date, "%Y%B")) %>% 
    group_by(YM) %>% 
    filter(date == dplyr::last(date)) %>% 
    ungroup() %>% 
    pull(date) %>% 
    unique()

# get the quarterly rebalance dates from the available dates
quarterly_rebalance <- rmsfuns::dateconverter(first(EOM_dates), last(EOM_datevec), "weekdayEOQ") 

# Create simple returns for all assets which have more than 3 years of prices and are available after the start date
comb_assets_return <- comb_assets %>% 
    filter(Ticker %in% comb_assets_3_years) %>% 
    filter(date >= Start_Date) %>% 
    group_by(Ticker) %>% 
    mutate(Return = Price/lag(Price) - 1) %>% 
    filter(date > dplyr::first(date)) %>% 
    select(-Price) %>%
    spread(Ticker, Return)

# Filter out all returns on the Quarterly rebalance dates
comb_assets_return_quarterly <- comb_assets_return %>% filter(date %in% quarterly_rebalance)

```


```{r}
# Imputation function from prac3

impute_missing_returns <- function(return_mat, impute_returns_method = "NONE"){
  # Make sure we have a date column called date:
  if( !"date" %in% colnames(return_mat) ) stop("No 'date' column provided in return_mat. Try again please.")

  # Note my use of 'any' below...
  # Also note that I 'return' return_mat - which stops the function and returns return_mat.
  if( impute_returns_method %in% c("NONE", "None", "none") ) {
    if( any(is.na(return_mat)) ) warning("There are missing values in the return matrix.. 
                                         Consider maybe using impute_returns_method = 'Drawn_Distribution_Own' / 'Drawn_Distribution_Collective'")
    return(return_mat)
  }

  if( impute_returns_method  == "Average") {

    return_mat <-
      return_mat %>% gather(Stocks, Returns, -date) %>%
      group_by(date) %>%
      mutate(Avg = mean(Returns, na.rm=T)) %>%
      mutate(Avg = coalesce(Avg, 0)) %>% # date with no returns - set avg to zero
      ungroup() %>%
      mutate(Returns = coalesce(Returns, Avg)) %>% select(-Avg) %>% spread(Stocks, Returns)

    # That is just so much easier when tidy right? See how I gathered and spread again to give back a wide df?
    return(return_mat)
  } else

    if( impute_returns_method  == "Drawn_Distribution_Own") {

      N <- nrow(return_mat)
      return_mat <-
        # DIY: see what density function does
        left_join(return_mat %>% gather(Stocks, Returns, -date),
                  return_mat %>% gather(Stocks, Returns, -date) %>% group_by(Stocks) %>%
                    mutate(Dens = list(density(Returns, na.rm=T))) %>%
                    summarise(set.seed(42), Random_Draws = list(sample(Dens[[1]]$x, N, replace = TRUE, prob=.$Dens[[1]]$y))),
                  by = "Stocks"
        ) %>%  group_by(Stocks) %>%
        # Random draw from sample:
        mutate(Returns = coalesce(Returns, Random_Draws[[1]][row_number()])) %>%
        select(-Random_Draws) %>% ungroup() %>% spread(Stocks, Returns)
      return(return_mat)
    } else

      if( impute_returns_method  == "Drawn_Distribution_Collective") {
        NAll <- nrow(return_mat %>% gather(Stocks, Returns, -date))
        # DIY: see what density function does
        return_mat <-
          bind_cols(
            return_mat %>% gather(Stocks, Returns, -date),
            return_mat %>% gather(Stocks, Returns, -date) %>%
              mutate(Dens = list(density(Returns, na.rm=T))) %>%
              summarise(set.seed(42), Random_Draws = list(sample(Dens[[1]]$x, NAll, replace = TRUE, prob=.$Dens[[1]]$y))) %>%
              unnest(Random_Draws)
          ) %>%
          mutate(Returns = coalesce(Returns, Random_Draws)) %>% select(-Random_Draws) %>% spread(Stocks, Returns)
        return(return_mat)
      } else

        if( impute_returns_method  == "Zero") {
          warning("This is probably not the best idea but who am I to judge....")
          return_mat[is.na(return_mat)] <- 0
          return(return_mat)
        } else
          stop("Please provide a valid impute_returns_method method. Options include:\n'Average', 'Drawn_Distribution_Own', 'Drawn_Distribution_Collective' and 'Zero'.")

  return_mat

}

# Impute missing values for return series
options(scipen = 999)
return_mat <- impute_missing_returns(comb_assets_return, impute_returns_method = "Drawn_Distribution_Collective")

sum(is.na(comb_assets_return))
# Since there are no missing values we do not need to impute

# Create returns matrix
return_mat_Nodate <- data.matrix(return_mat[, -1])
```



```{r}
HTT <- fitHeavyTail::fit_mvt(return_mat_Nodate)

mu <- return_mat %>% summarise(across(-date, ~prod(1+.)^(1/n())-1)) %>% purrr::as_vector()
Sigma <- HTT$cov

# Ensure order is the same for mu and Sigma (some optimizers are sensitive to ordering... :( )
mu <- mu[colnames(Sigma)] 
```


```{r}
# Purely for safety reasons, to avoid a non-positive definite matrix breaking your function...
Sigma <- as.matrix( Matrix::nearPD(Sigma)$mat)
```

Creating Amat and bvec

```{r}
# Create constraints

NStocks <- ncol(return_mat_Nodate)
NEquities <- 4
NCreditBonds <- 6
LB = 0.001 # No lower bound
UB = 0.4 # Upper bound for single asset
Equities = 0.6 # Equity Upper Bound
CreditBonds = 0.25 # Credit and Bonds Upper Bound
meq = 1 


# Make A Mat 
#Equities_mat <- rbind(matrix(0, nrow = (NStocks-NEquities), ncol = NEquities), -diag(NEquities))
#Credit_Bonds_mat <- rbind(matrix(0, (NStocks-NEquities-NCreditBonds), NCreditBonds), -diag(NCreditBonds), matrix(0, NEquities, NCreditBonds))

Equities_vec <- c(rep(0, NStocks-NEquities), -rep(1, NEquities))
Credit_Bonds_vec <- c(rep(0, NStocks-NEquities-NCreditBonds), -rep(1, NCreditBonds), rep(0, NEquities))

bvec <- c(1, rep(LB, NStocks), -rep(UB, NStocks), -CreditBonds, -Equities)
Amat <- cbind(1, diag(NStocks), -diag(NStocks), Credit_Bonds_vec, Equities_vec)


```


```{r}
# And now we are ready to combine this all into getting optimal weights given these constraints:
  
# we will use the quadprog package"
w.opt <- quadprog::solve.QP(Dmat = Sigma,
                            dvec = mu, 
                            Amat = Amat, 
                            bvec = bvec, 
                            meq = meq)$solution

result.QP <- tibble(stocks = colnames(Sigma), weight = w.opt) 

```

Now lets now calculate the EV, MinVol, ERC and Risk-eff optimizations from RiskPortfolios, while appending it together.

```{r}
optim_foo <- function(Type = "mv", mu, Sigma, bvec, Amat, printmsg = TRUE){

    Safe_Optim <- purrr::safely(quadprog::solve.QP)
    
    if(Type == "mv"){ 
        Opt_W <- Safe_Optim(Dmat = Sigma,
                            dvec = mu, 
                            Amat = Amat, 
                            bvec = bvec, 
                            meq = meq)
    }
    if(Type == "minvol"){
        Opt_W <- Safe_Optim(Dmat = Sigma,
                            dvec = rep(0, nrow(Sigma)), 
                            Amat = Amat,
                            bvec = bvec, 
                            meq = meq)
    }
    if(Type == "maxdecor"){
        Rho <- cov2cor(Sigma)
        Opt_W <- Safe_Optim(Dmat = Rho,
                            dvec = rep(0, nrow(Sigma)), 
                            Amat = Amat, 
                            bvec = bvec, 
                            meq = meq)
    }
    if(Type == "sharpe"){
        Amat[,1] <- mu
        Opt_W <- Safe_Optim(Dmat = Sigma,
                            dvec = rep(0, nrow(Sigma)), 
                            Amat = Amat, 
                            bvec = bvec, 
                            meq = meq)
    }

    if( is.null(Opt_W$error)){
        optimw <- tibble(Tickers = colnames(Sigma), weights = Opt_W$result$solution) %>% 
        # Take note:
        rename(!!Type := weights)
  
        if(printmsg)   optimw <- optimw %>% mutate(Result = glue::glue("Converged: {Type}"))
  
    } else {
        optimw <- tibble(Tickers = colnames(Sigma), weights = 1/ncol(Sigma)) %>% 
        # Take note:
        rename(!!Type := weights)
        
        if(printmsg)   optimw <- optimw %>% mutate(Result = glue::glue("Failed to Converge: {Type}"))
        }
     optimw
}


My_Weights <- optim_foo(Type = "maxdecor", mu, Sigma, bvec = bvec, Amat = Amat, printmsg = T)

My_Weights

```



```{r}
# Create Rolling function
Roll_optimizer <- function(return_mat, EOM_datevec, LookBackSel = 24, Amat, bvec){
    return_df_used <- return_mat %>% filter(date >= EOM_datevec %m-% months(LookBackSel))
    
    if(return_df_used %>% nrow() < LookBackSel) return(NULL) # return NULL effectively skips the iteration when binding....
    return_mat_Nodate <- data.matrix(return_mat[, -1])

    # Calculate Sigma and mu
    HTT <- fitHeavyTail::fit_mvt(return_mat_Nodate)
    mu <- HTT$mu
    Sigma <- HTT$cov
    
    Sigma <- as.matrix(Matrix::nearPD(Sigma)$mat)
    
    # Fit optimisation function with different types
    My_Weights <- left_join(
        optim_foo(Type = "mv", mu, Sigma, bvec, Amat, printmsg = F), 
        optim_foo(Type = "minvol", mu, Sigma, bvec, Amat, printmsg = F), 
        by = "Tickers") %>% 
            left_join(., optim_foo(Type = "maxdecor", mu, Sigma, bvec, Amat, printmsg = F), by = "Tickers") %>% 
                left_join(., optim_foo(Type = "sharpe", mu, Sigma, bvec, Amat, printmsg = F), by = "Tickers") %>% 
        mutate(date = EOM_datevec , Look_Back_Period = LookBackSel)
}

# Calculate optimal rolling weights for each type of portfolio optimization
Result <- quarterly_rebalance %>% map_df(~Roll_optimizer(return_mat, EOM_datevec = ., Amat = Amat, bvec = bvec, LookBackSel = 24))

Result
```

Graph result over time 

```{r}

```






















