---
output:
  md_document:
    variant: markdown_github
---

### Starting

I was working in the README's of the individual questions and neglected this one until too late. They all feel incompete after running out of time. 

I followed your code to get started, I hadn't nested your folders before and it worked well.

I did however get stuck on creating a GitHub repository from GitHub desktop as you I could not find a way to add git ignores from the get go. So I did restart as I accidentally uploaded my data files to Git.

```{r, eval = F}

fmxdat::make_project(Mac = TRUE)

Texevier::create_template_html(directory = "/Users/svenwellmann/Desktop/Masters Semester 1/DatSci/Practical/Solution/20850980/", template_name = "Question1")
Texevier::create_template_html(directory = "/Users/svenwellmann/Desktop/Masters Semester 1/DatSci/Practical/Solution/20850980/", template_name = "Question2")
Texevier::create_template_html(directory = "/Users/svenwellmann/Desktop/Masters Semester 1/DatSci/Practical/Solution/20850980/", template_name = "Question3")
```

# Question 1 Solution

```{r}

rm(list = ls()) # Clean your environment:
gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.
library(tidyverse)
list.files('Question1/code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```


### Question 1

#### Loading the data

```{r}
covid_data <- DataCollect("Question1/data/Covid/")
covid <- covid_data[[3]]
```

#### First plot

This plot firstly looks at Africa against the other continents for the cumulative cases and the cumulative deaths.

It shows that Africa at a counting level, falls way below the other continents. 


```{r}
g <- CumulativeLineGraph(covid, caseordeath = "case")
    
g
```

Second Plot in the paper creates a seven-day moving average of the new cases per day or deaths per day.

```{r}
g <- Seven_day_MA(covid, "case")
    
g
```

Third plot in the paper looks at countries demographics to assess what affects the Caste Fatality Ratio of Covid-19.

```{r}
g <- Case_Fatality_Ratio(covid, "population")
    
g
```


### Question 2




